---
title: "Getting started with uriahtalks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with uriahtalks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`uriahtalks` contains shared teaching data and presentation infrastructure used across Uriah Finkel's talks.

The first shared example is the smoking dataset. Each presentation should request only the view it needs while all views remain derived from the same canonical data.

```{r, eval = FALSE}
library(uriahtalks)

obs <- smoking_data("observational")
full <- smoking_data("full")
```

The observational view is intended for slides that work only with factual data. The full view exposes the underlying constructed data used to verify causal truths and keep related presentations consistent.

The package also provides shared visual defaults:

```{r, eval = FALSE}
library(ggplot2)

ggplot(obs, aes(x = x, fill = factor(a))) +
  geom_bar() +
  uriah_theme() +
  scale_fill_uriah()
```

For `reactable` tables:

```{r, eval = FALSE}
uriah_reactable(obs)
```

Before changing the canonical smoking data, run:

```{r, eval = FALSE}
check_smoking_data()
```

The package tests encode the invariants that need to remain stable across the conditional-exchangeability, causal-bounds, experimental-bounds, and mediation presentations.
